### 2017-04-01 paper/intro.tex
pass on dimension

Each dimension focuses on one aspect of our study.  The dimension
\textbf{potential} measures the potential of parallelization to make
an impact on testing costs.  In the limit, parallelization would be
fruitless if all projects used short-running test suites or if the
bulk of execution cost was dominated by a relatively small number of
tests in the suite. The dimension \textbf{usage} measures how often
open-source projects actually use parallelization schemes.  The
dimension \textbf{effectiveness} measures the observed impact of
parallelization (when used) on testing costs. The dimension
\textbf{perception} focuses on how developers involved in costly
projects not using test suite parallelization perceive this
technology.  Finally, the dimension \textbf{tradeoffs} evaluates the
issues and benefits associated with running test suites with different
parallel configurations (/modes).

>>>>

Each dimension focuses on one aspect of our study.  The dimension
\textbf{potential} measures the potential of parallelization to reduce
testing costs.  In the limit, parallelization would be fruitless if
all projects used short-running test suites or if the bulk of
execution cost was dominated by a relatively small number of tests in
the suite.  The dimension \textbf{effectiveness} measures the observed
impact of parallelization\Comment{~---~when used in selected
  open-source projects~---~} on testing costs.  Intuitively, benefits
are proportional to the cost reduction that parallelization brings.
In the limit, the overhead of spawning virtual machines or threads can
even result in added cost.  The dimension \textbf{adoption} evaluates
(i) how often open-source projects use parallelization schemes and
(ii) how developers involved in costly projects (not using test suite
parallelization) perceive this technology.  It is important to measure
resistance to the technology and its reasons.  Finally, the dimension
\textbf{tradeoff} evaluates the issues and benefits associated
with\Comment{running test suites with} different parallel
configurations.  The configuration choice can affect both test cost
and test flakiness.  Flakiness is caused by the non-determinism
resulted from running tests in different
schedulings. Paretto-efficient~\cite{hwang-masud-1979} configurations
can guide future developments in this area.
